How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-23 tse-paper/content.tex
replace lots of ours

Despite its central role for helping developers and for enabling
applications for on-ward processing of build logs,
the process of how to
automatically analyze build logs has thus far received little
attention as a separate research topic, bringing us to our first
research question:
\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
1}}
What are the state-of-the-research techniques to analyze build logs?
\end{simplebox}

To answer this question, we start our investigation by performing an
extensive literature study (\Cref{fig:overview}).
It shows that
less than half of the 61 works which rely on build log analysis
describe in detail how they performed it.
Even fewer
made their implementation available.
The literature
survey identifies three prevalent strategies to
analyze build logs: Using 1) a set of
manually curated regular expressions,
similar to TravisTorrent~\cite{beller2017oops},
2) information
retrieval techniques,
% TODO: Can you shortly explain the technique here?
and 3) a list of search keywords
to identify regions of interest in the build log.

@@

To answer this question, in the second step of our study
(\Cref{fig:overview}), we build and compare three
implementations that each stand protoypical for one of the idenitied
strategies to analyze build logs:

@@

\subsection{Study Selection}
\Cref{fig:lit-survey} presents an overview of our study selection
process.
Since the field of build log analysis is relatively young, we
surveyed as broad a population of scientific material as possible.
We did not limit our sources to specific Software Engineering
venues~\cite{petersen2015guidelines}, but survey all sources
monitored by Google Scholar, including Bachelor's theses, Master's
theses, and academic slide decks.
We use Google Scholar as opposed to Scopus or
other databases because it is the search engine for academic articles with
the broadest and most current index, including preprints.

An initial Google Scholar search for variations of ``build log''
returned more than 2.2 million results (2020-03-15), many of which stem
from unrelated fields such as construction and wood working.
We refined our search criteria to exclude such obvious
non-related fields and also to exclude works on systems
or event logs (see \Cref{sec:system-log-analysis}).
This left us with 1,552 search results
(2020-03-15).
% Our replication package documents the full search
% queries~\cite{brandt2020chunk-replication}.
To make handling so many search results feasible, we employed a
three-pass filtering strategy:

First, we filtered articles based on (a) their title and (b) the
contextual information Google Scholar displayed.
We included works at large that seemed to bear a resemblance to software
engineering and building software.
We excluded works written in a language unintelligible to the authors
(i.e., not English or German), which disregarded fewer than 1\% of search
hits.
We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query.
We removed further duplicates based on the title and were
left with 256 (16\%) of the original search results.
% removed duplicates of data extraction pass already here
With these 256 remaining articles, we followed a backward snowball
sampling for related work.
If an article referenced a new work in the context
of build log analysis, we added the new one to our literature set.
This added five articles (eight before
duplicate elimination), leading to a total of 261
works.

Subsequently, we performed a second, finer filter phase by downloading the
full text of the works, reading their abstracts, and searching the
full text
for the occurrence of ``log.''
If a work showed traces of
working with build logs, we included it in our survey.
In total, we
were left with 87 works after the second filtering phases.

@@

% TODO remove first part of this paragraph?
Sometimes, aspects separate from the build log analysis motivate
this limitation to a specific build tool.
For example, Shi et al.~\cite{shi2018evaluating} focussed on Maven
build logs because they also chose the PIT tool to calculate coverage
and mutation score.
A larger amount of the articles within our survey, however, limit
themselves to few build tools because their log format varies and
therefore ``parsers must be specialized to each build and test
framework''~\cite{tomassi2019bugswarm}.

@@

Our evaluation of the three chunk retrieval techniques is done on the
\emph{LogChunks} data set because it encompasses a broad range of
build environments which enables us to measure the generic
applicability of our techniques.
The targeted chunks are describing error messages or
``the reason the build failed,'' which was also the information
most targeted by the articles in our survey.

@@

This section introduces key concepts of the three chunk retrieval
techniques we study in this article, namely program synthesis by
example (PBE), common text similarity (CTS), and keyword search (KWS).
In addition, we present our comparison baseline of random line
retrieval (RLR), illustrate the techniques on a concrete example
of log chunks and sketch out their implementation.

% TODO this is not enough for Table 3.
Where does it come from?
% How did it originate? Also: never single sentence abstracts
\Cref{tab:ctr} shows a comparison of the implemented techniques.

@@

\subsubsection{Configuration}
To configure chunk retrieval through text similarity we chose to use
the same concept of examples as for PBE
% Moritz: your question was: More details on this.
% How do you
% 'apply' VSM? On what?
% all the following sentences in this subsubsection describe our way
% of determining text similarity which as far as I understand and
% Annibale said is the VSM.
% word tokens, tf-idf, similarity measure
% I added a "as follows", think that is enough for explanation?
% Moritz: I think it is good, but the VSM is still unexplained.
We need a
% (at least) 1-sentence introduction to it, at its first reference
% TODO Moritz: I removed all other references, this is now the first one.
% I hope I got your comment right and now the first and only reference
% is explained :)
and apply the Vector Space Model~\cite{schutze2008introduction}
as follows:
The lines of the output strings of the training examples define our
search query.
The algorithm splits the search query into single lines and
identifies tokens, in our case words.
Then we build a
document-term-frequency matrix over the lines from the search query
and prune very often or very rarely appearing words.
Finally, the
algorithm applies TF-IDF to the matrix, a best practice for natural
language queries~\cite{lee1997document}.

@@

When PBE is trained with these two examples, it produces
a regular expression program similar to the one presented in
\Cref{lst:prose-program-simplified}.
The retrieval
starts after a colon and a line separator and before a capital
letter.
It ends before two line separators,
which is consistent with the two example
chunks from \Cref{lst:chunk-example}.
This shows, that the characters structuring the text around the chunk are
crucial for regular expressions to identify a log chunk.
In fact, if the third example from \Cref{lst:chunk-example-3},
which has a
different structural representation, is added to the training set,
PBE is not able to synthesize a program and returns
``\texttt{no program found}.''
We later express this difference in structural representation through
dividing log chunks into \emph{structural categories}.
The chunks from \Cref{lst:chunk-example}
are in the \emph{same structural category}, while the chunk from
\Cref{lst:chunk-example-3} is in a
\emph{different structural category}.
The results of our empirical comparison study on the chunk retrieval
techniques
show that the structural representation of the targeted chunk greatly
influences
the performance of the chunk retrieval techniques.

@@

\subsection{Tool Implementation}
For our comparison study, we implemented each of the chunk retrieval
techniques and a unifying interface.
The unified interface is implemented in Ruby and
calls the separate technique implementations over the command line.
We implemented PBE in C\# based on the Microsoft PROSE
library~\cite{prose2019webpage} and CTS, KWS, and RLR using
R and the text2vec library~\cite{text2vec2019webpage}.

@@

\begin{figure*}[tb]
	\centering
	\includegraphics[width=\textwidth, trim={1.6cm 1.6cm 0.2cm 5.6cm},
  clip]{img/study.pdf}
	\caption{Design of our technique comparison study.}
	\label{fig:study}
\end{figure*}

@@

\subsection{Study Process}
% TODO: I think you need to introduce a concept that makes clear what one
% ``folder'' consists of ...
% TODO: What does this mean -- we begin by? Aren't we perhaps missing that
% we operate on all repos in LogChunks?
We begin by selecting all examples in \emph{LogChunks}
that correspond to one GitHub repository---and thus the
% TODO () is meant to reference the figure, but this the figure is not
%actually mentioned.
same build environment (1).
% TODO: What does this mean? Of what nature are the examples? How were
%they chosen?
% Isn't it rather the case that for each repository, we built traning
%ets of size 1, 2,
% ...
%5 build logs?
One to five examples make up the training set (2).
% TODO passive ...
We vary its size to measure how many examples are needed to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).
% TODO: The example? why only one? And what is an example? An example
%build log?
% Then it would be good to say so.
The example chronologically after the training set makes up the
test set (3).
In this way, we train on examples from past build logs and test on
more recent logs.
We chose a test set size of 1, as users of our techniques
should receive reliable results on every build log they analyze.
% TODO and why is this important? Doesn't everyone want such stability
of results?
In the next step, we configure a chunk retrieval technique with
the examples from the training set (4) and apply the technique to the
training set (5), which produces the retrieval output (6).
Based on this, we collect the following measurements (7):
the size of the training set (\textbf{RQ2.1}),
the number of structural categories in the training
set (\textbf{RQ2.2}),
the lines of the retrieval output ($\mathit{RetrievedLines}$),
and our oracle: the output defined in the test example
($\mathit{DesiredLines}$).
From these we calculate accuracy metrics (\textbf{RQ2.3}):

@@

% TODO decision tree -> recommendation schema? You can use the more
%specific decision
% tree when referencing the figure.
For the interpretation of our study results, we look at each chunk
retrieval technique separately.
We give recommendations for
which types of log chunks and how many training examples
each technique is suited, as well as
how their output can be used further.
Following that, we discuss
which of these criteria should influence the decision to use a certain
chunk retrieval technique most.
Based on our empirical comparison, we present a
decision tree between the three techniques we investigated.

@@

When the training examples are of the same structure, one or two
two training examples are enough input for PROSE to synthesize a regular
expression program with good recall.
In our study, additional training
examples from the same structural category
did not improve the chunk retrieval.
% Moritz: Why uncomment the following? Is it not true?
% I think it is crucial.
% In fact, unless they
% were in some sense redundant, adding training examples above that even
% hindered the applicability of PBE.
% TODO: it's true.
Though this is because of the structural categories
% which we discuss not in this paragraph but the one above.

@@

The number of training examples had no noticeable influence on
precision or recall in our study.
Information retrieval techniques
like text similarity commonly learn on a higher number of examples
than used for our study.
Future work is needed to investigate how many
examples yield improvements in the chunk retrieval over a single
training example.

@@

\subsection{Recommendation of Suitable Techniques}
% TODO Make intro less generic?
After discussing the three chunk retrieval techniques separately we
now want to unify our results into one recommendation scheme.
% TODO Try to inductiviely let the figure emerge from the text, not this
% ``here is the figure; eat it''.
% C: ``How should I do this?''
% Already a better solution would be at the end of this section: We
% summarized these conditions in the decision tree in Fig ...
\Cref{fig:crt-recommendation} presents a decision tree
to answer our second research question;
If researchers or developers want to retrieve chunks from build logs,
they can follow the decision tree to identify the technique
suited best for their use case.
The decision tree is built up of questions
which either lead to more questions or to a leaf node containing a
recommended technique.

@@

% TODO this is very nice again, perhaps a tiny bit on the trivial side.
% Do reference Figure 17 more, thoguh
To illustrate how one would use our decision tree to find a suitable
chunk retrieval technique we describe two concrete examples: a software
team
wanting to monitor their build performance and a
researcher investigating why builds fail.

In our first example, a software development team wants to monitor
the performance of the phases within their CI build.
They are using
Travis CI, which measures the duration of build phases and documents
this within the build log.
As all log statements that report timing
measurements are formatted the same way, the targeted log chunks are
from one structural category.
Therefore, the development team can use
PBE to retrieve the duration of a build phase.

In our second example, a researcher wants to investigate whether a small
or large group of test cases
causes build failures.
They gather
CI build logs from various projects.
The task of the researcher is to extract the names of the
failing test cases from each build log.
When they use our
recommendation scheme to select a chunk retrieval technique, they
first have to estimate how uniform the representation of the failing
test cases is in the investigated build logs.
As the researcher is
covering a wide range of test tools, the
log chunks they target are in various, non-predictable structural
representations.
The next question is whether they value precision
over recall.
As they have to manually inspect the results of both CTS
and KWS, they choose recall over precision to avoid having to inspect
the whole log in case the relevant information chunk was not
retrieved.
Therefore, our decision tree recommends the researcher to use KWS\@.

@@

\textbf{Implementation.}
Our results depend on the implementation of the investigated chunk
retrieval techniques and the libraries we used.
Our implementation of
PBE is based on the program synthesis provided by PROSE\@.
The
idiosyncrasies of this framework influence our PBE results.
Other
frameworks similar to PROSE might have somewhat different strengths
and weaknesses.
For example, the need for examples from a single
structural category stems from the fact that PROSE cannot learn
regular expression programs with arbitrary boolean conjunctions and
disjunctions~\cite{mayer2015user}.
PROSE introduced this constraint to
keep the synthesis performance reasonable.
At the same time, this is
clearly a current theoretical challenge of all PBE implementations,
and we therefore attribute it to the technique itself, rather than the
specific implementation.

@@

\textbf{Data Set.}
The outcomes of our comparison study are highly dependent on the build
logs from the \emph{LogChunks} data set.
It consists of build
logs from open source projects and therefore it is not clear whether
our results apply to industry projects that use build tools
not popular in open source development.
However, since \emph{LogChunks} covers a wide array of build tools and
programming languages,
we believe that our findings do generalize.
We collected build logs from Travis CI.
Yet, the format of the log chunk we chose
for our evaluation is largely independent of Travis CI\@.
This
is because the reason the build failed is described within the build
logs by the tools themselves and not the Travis CI environment.

\textbf{Training Set Size.}
Especially the results for CTS might be influenced by the fact that we
only trained on one to five examples.
We chose this small training set
size as the training examples have to be provided per repository and
we expect a developer to not want to provide more examples than the
small numbers we evaluated on.
The fact that PBE and CTS performed best with already two training
examples shows that our training set size is large enough to
compare the three techniques we presented.

@@

There are various future research opportunities based on our work:

>>>>

Despite its central role for helping developers and for enabling
applications for on-ward processing of build logs,
the process of how to
automatically analyze build logs has thus far received little
attention as a separate research topic, bringing us to the first
research question:
\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
1}}
What are the state-of-the-research techniques to analyze build logs?
\end{simplebox}

To answer this question, we start the investigation by performing an
extensive literature study (\Cref{fig:overview}).
It shows that
less than half of the 61 works which rely on build log analysis
describe in detail how they performed it.
Even fewer
made their implementation available.
The literature
survey identifies three prevalent strategies to
analyze build logs: Using 1) a set of
manually curated regular expressions,
similar to TravisTorrent~\cite{beller2017oops},
2) information
retrieval techniques,
% TODO: Can you shortly explain the technique here?
and 3) a list of search keywords
to identify regions of interest in the build log.

@@

To answer this question, in the second step of the study
(\Cref{fig:overview}), we build and compare three
implementations that each stand protoypical for one of the idenitied
strategies to analyze build logs:

@@

\subsection{Study Selection}
\Cref{fig:lit-survey} presents an overview of the study selection
process.
Since the field of build log analysis is relatively young, we
surveyed as broad a population of scientific material as possible.
We did not limit the sources to specific Software Engineering
venues~\cite{petersen2015guidelines}, but survey all sources
monitored by Google Scholar, including Bachelor's theses, Master's
theses, and academic slide decks.
We use Google Scholar as opposed to Scopus or
other databases because it is the search engine for academic articles with
the broadest and most current index, including preprints.

An initial Google Scholar search for variations of ``build log''
returned more than 2.2 million results (2020-03-15), many of which stem
from unrelated fields such as construction and wood working.
We refined the search criteria to exclude such obvious
non-related fields and also to exclude works on systems
or event logs (see \Cref{sec:system-log-analysis}).
This left us with 1,552 search results
(2020-03-15).
% Our replication package documents the full search
% queries~\cite{brandt2020chunk-replication}.
To make handling so many search results feasible, we employed a
three-pass filtering strategy:

First, we filtered articles based on (a) their title and (b) the
contextual information Google Scholar displayed.
We included works at large that seemed to bear a resemblance to software
engineering and building software.
We excluded works written in a language unintelligible to the authors
(i.e., not English or German), which disregarded fewer than 1\% of search
hits.
We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query.
We removed further duplicates based on the title and were
left with 256 (16\%) of the original search results.
% removed duplicates of data extraction pass already here
With these 256 remaining articles, we followed a backward snowball
sampling for related work.
If an article referenced a new work in the context
of build log analysis, we added the new one to the literature set.
This added five articles (eight before
duplicate elimination), leading to a total of 261
works.

Subsequently, we performed a second, finer filter phase by downloading the
full text of the works, reading their abstracts, and searching the
full text
for the occurrence of ``log.''
If a work showed traces of
working with build logs, we included it in the survey.
In total, we
were left with 87 works after the second filtering phases.

@@

% TODO remove first part of this paragraph?
Sometimes, aspects separate from the build log analysis motivate
this limitation to a specific build tool.
For example, Shi et al.~\cite{shi2018evaluating} focussed on Maven
build logs because they also chose the PIT tool to calculate coverage
and mutation score.
A larger amount of the articles within the survey, however, limit
themselves to few build tools because their log format varies and
therefore ``parsers must be specialized to each build and test
framework''~\cite{tomassi2019bugswarm}.

@@

Our evaluation of the three chunk retrieval techniques is done on the
\emph{LogChunks} data set because it encompasses a broad range of
build environments which enables us to measure the generic
applicability of the techniques.
The targeted chunks are describing error messages or
``the reason the build failed,'' which was also the information
most targeted by the articles in our survey.

@@

This section introduces key concepts of the three chunk retrieval
techniques we study in this article, namely program synthesis by
example (PBE), common text similarity (CTS), and keyword search (KWS).
In addition, we present a comparison baseline of random line
retrieval (RLR), illustrate the techniques on a concrete example
of log chunks and sketch out their implementation.

% TODO this is not enough for Table 3.
%Where does it come from?
% How did it originate? Also: never single sentence abstracts
\Cref{tab:ctr} shows a comparison of the implemented techniques.

@@

\subsubsection{Configuration}
To configure chunk retrieval through text similarity we chose to use
the same concept of examples as for PBE
% Moritz: your question was: More details on this.
% How do you
% 'apply' VSM? On what?
% all the following sentences in this subsubsection describe our way
% of determining text similarity which as far as I understand and
% Annibale said is the VSM.
% word tokens, tf-idf, similarity measure
% I added a "as follows", think that is enough for explanation?
% Moritz: I think it is good, but the VSM is still unexplained.
%We need a
% (at least) 1-sentence introduction to it, at its first reference
% TODO Moritz: I removed all other references, this is now the first one.
% I hope I got your comment right and now the first and only reference
% is explained :)
and apply the Vector Space Model~\cite{schutze2008introduction}
as follows:
The lines of the output strings of the training examples define our
search query.
The algorithm splits the search query into single lines and
identifies tokens, in this case words.
Then we build a
document-term-frequency matrix over the lines from the search query
and prune very often or very rarely appearing words.
Finally, the
algorithm applies TF-IDF to the matrix, a best practice for natural
language queries~\cite{lee1997document}.

@@

When PBE is trained with these two examples, it produces
a regular expression program similar to the one presented in
\Cref{lst:prose-program-simplified}.
The retrieval
starts after a colon and a line separator and before a capital
letter.
It ends before two line separators,
which is consistent with the two example
chunks from \Cref{lst:chunk-example}.
This shows, that the characters structuring the text around the chunk are
crucial for regular expressions to identify a log chunk.
In fact, if the third example from \Cref{lst:chunk-example-3},
which has a
different structural representation, is added to the training set,
PBE is not able to synthesize a program and returns
``\texttt{no program found}.''
We later express this difference in structural representation through
dividing log chunks into \emph{structural categories}.
The chunks from \Cref{lst:chunk-example}
are in the \emph{same structural category}, while the chunk from
\Cref{lst:chunk-example-3} is in a
\emph{different structural category}.
The results of the empirical comparison study on the chunk retrieval
techniques
show that the structural representation of the targeted chunk greatly
influences
the performance of the chunk retrieval techniques.

@@

\subsection{Tool Implementation}
For the comparison study, we implemented each of the chunk retrieval
techniques and a unifying interface.
The unified interface is implemented in Ruby and
calls the separate technique implementations over the command line.
We implemented PBE in C\# based on the Microsoft PROSE
library~\cite{prose2019webpage} and CTS, KWS, and RLR using
R and the text2vec library~\cite{text2vec2019webpage}.

@@

\begin{figure*}[tb]
	\centering
	\includegraphics[width=\textwidth, trim={1.6cm 1.6cm 0.2cm 5.6cm},
  clip]{img/study.pdf}
	\caption{Design of the technique comparison study.}
	\label{fig:study}
\end{figure*}

@@

\subsection{Study Process}
% TODO: I think you need to introduce a concept that makes clear what one
% ``folder'' consists of ...
% TODO: What does this mean -- we begin by? Aren't we perhaps missing that
% we operate on all repos in LogChunks?
We begin by selecting all examples in \emph{LogChunks}
that correspond to one GitHub repository---and thus the
% TODO () is meant to reference the figure, but this the figure is not
%actually mentioned.
same build environment (1).
% TODO: What does this mean? Of what nature are the examples? How were
%they chosen?
% Isn't it rather the case that for each repository, we built traning
%ets of size 1, 2,
% ...
%5 build logs?
One to five examples make up the training set (2).
% TODO passive ...
We vary its size to measure how many examples are needed to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).
% TODO: The example? why only one? And what is an example? An example
%build log?
% Then it would be good to say so.
The example chronologically after the training set makes up the
test set (3).
In this way, we train on examples from past build logs and test on
more recent logs.
We chose a test set size of 1, as users of the techniques
should receive reliable results on every build log they analyze.
% TODO and why is this important? Doesn't everyone want such stability
%of results?
In the next step, we configure a chunk retrieval technique with
the examples from the training set (4) and apply the technique to the
training set (5), which produces the retrieval output (6).
Based on this, we collect the following measurements (7):
the size of the training set (\textbf{RQ2.1}),
the number of structural categories in the training
set (\textbf{RQ2.2}),
the lines of the retrieval output ($\mathit{RetrievedLines}$),
and the oracle: the output defined in the test example
($\mathit{DesiredLines}$).
From these we calculate accuracy metrics (\textbf{RQ2.3}):

@@

% TODO decision tree -> recommendation schema? You can use the more
%specific decision
% tree when referencing the figure.
For the interpretation of the study results, we look at each chunk
retrieval technique separately.
We give recommendations for
which types of log chunks and how many training examples
each technique is suited, as well as
how their output can be used further.
Following that, we discuss
which of these criteria should influence the decision to use a certain
chunk retrieval technique most.
Based on the empirical comparison, we present a
decision tree between the three techniques we investigated.

@@

When the training examples are of the same structure, one or two
two training examples are enough input for PROSE to synthesize a regular
expression program with good recall.
In the study, additional training
examples from the same structural category
did not improve the chunk retrieval.
% Moritz: Why uncomment the following? Is it not true?
% I think it is crucial.
% In fact, unless they
% were in some sense redundant, adding training examples above that even
% hindered the applicability of PBE.
% TODO: it's true.
Though this is because of the structural categories
% which we discuss not in this paragraph but the one above.

@@

The number of training examples had no noticeable influence on
precision or recall.
Information retrieval techniques
like text similarity commonly learn on a higher number of examples
than we chose in the study.
Future work should investigate how many
examples yield improvements in the chunk retrieval over a single
training example.

@@

\subsection{Recommendation of Suitable Techniques}
% TODO Make intro less generic?
After discussing the three chunk retrieval techniques separately we
now want to unify the results into one recommendation scheme.
% TODO Try to inductiviely let the figure emerge from the text, not this
% ``here is the figure; eat it''.
% C: ``How should I do this?''
% Already a better solution would be at the end of this section: We
% summarized these conditions in the decision tree in Fig ...
\Cref{fig:crt-recommendation} presents a decision tree
to answer the second research question;
If researchers or developers want to retrieve chunks from build logs,
they can follow the decision tree to identify the technique
suited best for their use case.
The decision tree is built up of questions
which either lead to more questions or to a leaf node containing a
recommended technique.

@@

% TODO this is very nice again, perhaps a tiny bit on the trivial side.
% Do reference Figure 17 more, thoguh
To illustrate how one would use the decision tree to find a suitable
chunk retrieval technique we describe two concrete examples: a software
team
wanting to monitor their build performance and a
researcher investigating why builds fail.

In the first example, a software development team wants to monitor
the performance of the phases within their CI build.
They are using
Travis CI, which measures the duration of build phases and documents
this within the build log.
As all log statements that report timing
measurements are formatted the same way, the targeted log chunks are
from one structural category.
Therefore, the development team can use
PBE to retrieve the duration of a build phase.

In the second example, a researcher wants to investigate whether a small
or large group of test cases
causes build failures.
They gather
CI build logs from various projects.
The task of the researcher is to extract the names of the
failing test cases from each build log.
When they use our
recommendation scheme to select a chunk retrieval technique, they
first have to estimate how uniform the representation of the failing
test cases is in the investigated build logs.
As the researcher is
covering a wide range of test tools, the
log chunks they target are in various, non-predictable structural
representations.
The next question is whether they value precision
over recall.
As they have to manually inspect the results of both CTS
and KWS, they choose recall over precision to avoid having to inspect
the whole log in case the relevant information chunk was not
retrieved.
Therefore, the decision tree recommends the researcher to use KWS\@.

@@

\textbf{Implementation.}
Our results depend on the implementation of the investigated chunk
retrieval techniques and the libraries we used.
Our implementation of
PBE is based on the program synthesis provided by PROSE\@.
The
idiosyncrasies of this framework influence the PBE results.
Other
frameworks similar to PROSE might have somewhat different strengths
and weaknesses.
For example, the need for examples from a single
structural category stems from the fact that PROSE cannot learn
regular expression programs with arbitrary boolean conjunctions and
disjunctions~\cite{mayer2015user}.
PROSE introduced this constraint to
keep the synthesis performance reasonable.
At the same time, this is
clearly a current theoretical challenge of all PBE implementations,
and we therefore attribute it to the technique itself, rather than the
specific implementation.

@@

\textbf{Data Set.}
The outcomes of the comparison study are highly dependent on the build
logs from the \emph{LogChunks} data set.
It consists of build
logs from open source projects and therefore it is not clear whether
our results apply to industry projects that use build tools
not popular in open source development.
However, since \emph{LogChunks} covers a wide array of build tools and
programming languages,
we believe that the findings do generalize.
We collected build logs from Travis CI.
Yet, the format of the log chunk we chose
for the evaluation is largely independent of Travis CI\@.
This
is because the reason the build failed is described within the build
logs by the tools themselves and not the Travis CI environment.

\textbf{Training Set Size.}
Especially the results for CTS might be influenced by the fact that we
only trained on one to five examples.
We chose this small training set
size as the training examples have to be provided per repository and
we expect a developer to not want to provide more examples than the
small numbers we evaluated on.
The fact that PBE and CTS performed best with already two training
examples shows that the training set size is large enough to
compare the three techniques we presented.

@@

There are various future research opportunities based on the
work we presented:
